\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}

\begin{thebibliography}{1}

\bibitem {react}
Meta Platforms Inc (2023), \emph{React Tutorial}, URL: \url{https://reactjs.org/}, truy cập lần cuối: 17/12/2023.

\bibitem{springboot}
LTS EDU (2023), \emph{Java Spring Boot là gì ? Java Spring MVC là gì ? Spring Framework là gì ?}, URL: \url{https://lotusacademy.edu.vn/blog/java-spring-boot-la-gi-java-spring-mvc-la-gi-spring-framework-la-gi-256}, truy cập lần cuối: 17/12/2023.

\bibitem{nodejs}
NodeJS (2023), \emph{About Node.js}, URL: \url{https://nodejs.org/en/about}, truy cập lần cuối: 17/12/2023.

\bibitem{docker}
Docker (2023), \emph{Docker docs}, URL: \url{https://docs.docker.com/}, truy cập lần cuối: 17/12/2023.

\bibitem{postgres}
PostgreSQL (2023), \emph{PostgreSQL: The World's Most Advanced Open Source Relational Database}, URL: \url{https://www.postgresql.org/}, truy cập lần cuối: 17/12/2023.

\bibitem{terraform}
Terraform by HashiCorp (2023), \emph{Terraform Docs}, URL: \url{https://developer.hashicorp.com/terraform?product_intent=terraform}, truy cập lần cuối: 17/12/2023.

\bibitem{terraform_2}
Tran Phuc Hau (23/4/2023), \emph{Terraform là gì?}, URL: \url{https://www.alibabacloud.com/blog/terraform-l%C3%A0-g%C3%AC-_599921}, truy cập lần cuối: 17/12/2023.

\bibitem{k8s}
Kubernetes - Tài liệu (2023), \emph{Kubernetes là gì}, URL: \url{https://kubernetes.io/vi/docs/concepts/overview/what-is-kubernetes}, truy cập lần cuối: 17/12/2023.

\bibitem{eks}
AWS (2023), \emph{Dịch vụ Kubernetes linh hoạt Amazon}, URL: \url{https://aws.amazon.com/vi/eks/}, truy cập lần cuối: 17/12/2023.

\bibitem{aks}
Microsoft Learn (2023), \emph{What is Azure Kubernetes Service?}, URL: \url{https://learn.microsoft.com/en-us/azure/aks/intro-kubernetes}, truy cập lần cuối: 17/12/2023.

\bibitem{rabbitmq}
Gabor Olah, \emph{An introduction to RabbitMQ - What is RabbitMQ?}, URL: \url{https://www.erlang-solutions.com/blog/an-introduction-to-rabbitmq-what-is-rabbitmq/}, truy cập lần cuối: 17/12/2023.

\bibitem{availability_n_scalability}
Microsoft Learn (2023), \emph{Describe the benefits of high availability and scalability in the cloud}, URL: \url{https://learn.microsoft.com/en-us/training/modules/describe-benefits-use-cloud-services/2-high-availability-scalability-cloud}, truy cập lần cuối: 17/12/2023.

\bibitem{mono_vs_ms}
Microsoft Learn (2023), \emph{Decompose a monolithic application into a microservices architecture}, URL: \url{https://learn.microsoft.com/en-us/training/modules/microservices-architecture/}, truy cập lần cuối 17/12/2023.

\bibitem{case_aks_1}
Microsoft Learn (2023), \emph{Microservices architecture on Azure Kubernetes Service}, URL: \url{https://learn.microsoft.com/en-us/azure/architecture/reference-architectures/containers/aks-microservices/aks-microservices}, truy cập lần cuối 17/12/2023.


\bibitem{case_aks_2}
Microsoft Learn (2023), \emph{Advanced Azure Kubernetes Service (AKS) microservices architecture}, URL: \url{https://learn.microsoft.com/en-us/azure/architecture/reference-architectures/containers/aks-microservices/aks-microservices-advanced/}, truy cập lần cuối 17/12/2023.

\bibitem{case_aks_3}
Microsoft Learn (2023), \emph{Magento e-commerce platform in Azure Kubernetes Service}, URL: \url{https://learn.microsoft.com/en-us/azure/architecture/example-scenario/magento/magento-azure}, truy cập lần cuối 17/12/2023.

\bibitem{case_aws_1}
Saurabh Shrivastava (16/01/2018), \emph{Scale Your Web Application — One Step at a Time}, URL: \url{https://aws.amazon.com/vi/blogs/architecture/scale-your-web-application-one-step-at-a-time/}, truy cập lần cuối 17/12/2023.

\bibitem{case_aws_2}
Adritano Cataluddi (08/02/2023), \emph{Scaling PHP Applications on AWS}, URL: \url{https://www.logicata.com/blog/scaling-php-applications-on-aws/}, truy cập lần cuối 17/12/2023.

\bibitem{case_aws_3}
Stacksimplify (2023), \emph{Microservices Deployment on EKS}, URL: \url{https://www.stacksimplify.com/aws-eks/microservices-on-aws-eks/learn-to-deploy-microservices-on-aws-eks/}, truy cập lần cuối 17/12/2023.

\bibitem{minikube}
Minikube (2023), \emph{Documentation}, URL: \url{https://minikube.sigs.k8s.io/docs/}, truy cập lần cuối 17/12/2023.

\bibitem{Autoscale Apps}
Daniel Weibel (OCTOBER 2019), \emph{How to autoscale apps on Kubernetes with custom metrics}, URL: \url{https://learnk8s.io/autoscaling-apps-kubernetes}, truy cập lần cuối 08/01/2024.

\end{thebibliography}